Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2015-08-23 doc/GMP2015/revision_3/s02_preliminaries.tex
Lots of work on Revision 3, getting close.

\ClearMyMinHeight
\SetMyMinHeight{.4}{../../img/svg/3xc2c3}
\SetMyMinHeight{.3}{../../img/svg/3xc2c3_comdrp}
\SetMyMinHeight{.3}{../../img/svg/3xc2c3_candrp}

\begin{figure*}\centering%
  %
  \begin{subfigure}{0.4\linewidth}\centering
    \includegraphics[height=\myMinHeight]{../../img/svg/3xc2c3}
    \caption{}\label{fig:demo_graph:graph}
  \end{subfigure}%
  %
  \hfill
  \begin{subfigure}{0.3\linewidth}\centering
    \includegraphics[height=\myMinHeight]{../../img/svg/3xc2c3_comdrp}
    \caption{}\label{fig:demo_graph:comdrp}
  \end{subfigure}%
  %
  \hfill
  \begin{subfigure}{0.3\linewidth}\centering
    \includegraphics[height=\myMinHeight]{../../img/svg/3xc2c3_candrp}
    \caption{}\label{fig:demo_graph:candrp}
  \end{subfigure}%
  %
  \caption{(\ref{fig:demo_graph:graph}) A graph, $G_{demo}$, used to illustrate concepts throughout this and the next section. (\ref{fig:demo_graph:comdrp}) The complete DR-plan of $G_{demo}$, i.e.\ $ComDRP(G_{demo})$. Dashed lines indicate that the children repeat the same pattern as the others shown on this level. The children of triangles (3 edges) are omitted. (\ref{fig:demo_graph:candrp}) The canonical DR-plan of $G_{demo}$, which is optimal (see Section~\ref{sec:DRP}), i.e.\ $OptDRP(G_{demo})$. The children of triangles are omitted.}
  \label{fig:demo_graph}
\end{figure*}%

@@

% \begin{definition}\label{def:drp}
%     The \dfn{decomposition-recombination \mbox{(DR-)} plan} \cite{hoffman2001decompositionI} of graph $G$, $\drp{G}$, is defined as a forest that has the following properties:
%     \begin{enumerate}
%         \item Each node represents/contains/is a rigid subgraph of $G$.
%         % \item For a node, $C$, that is  a non-trivial graph, its $N$
%         % children, $C_1, \ldots, C_N$, are rigid vertex-maximal proper
%         % subgraphs of $C$.
%         \item The children $C_1,\ldots,C_N$ of a node $C$ satisfy $\bigcup_{i=1}^N{C_i}=C$.
%         \item A leaf node is a single edge. A \dfn{trivial} graph is empty or a single vertex. Note that a trivial graph is not isostatic.
%         \item A root node is a vertex-maximal rigid subgraph of $G$.
%     \end{enumerate}
% %
%     % It can also be described recursively as: the root is $G$, its children are the trivial subgraphs and the DR-plans of its wellconstrained vertex-maximal proper subgraphs whose union is $G$ itself.
% %
%     A DR-plan is \dfn{complete} if it satisfies an additional property: for a non-leaf node $C$, its children are all of the rigid vertex-maximal proper subgraphs of $C$. This makes Property 2 implicit.
%   %and in fact, $C$ contains all the edges in the union of its children as well.
%   We denote a complete DR-plan of $G$ as $\comdrp{G}$.

@@

% We begin with the definition of a general DR-plan and also introduce two specific kinds of DR-plans.

\begin{definition}\label{def:drp}
    A \dfn{decomposition-recombination \mbox{(DR-)} plan}~\cite{hoffman2001decompositionI} of graph $G$ is defined as a forest that has the following properties:
    \begin{enumerate}
        \item Each node represents a rigid subgraph of $G$.
        \item A root node is a vertex-maximal rigid subgraph of $G$.
        \item A node is the subgraph of $G$ induced by the union of its children.
        \item A leaf node is a single edge.
    \end{enumerate}
\end{definition}

\begin{definition}
    A DR-plan is \dfn{complete} if it satisfies an additional property: for a non-leaf node $C$, its children are all of the rigid vertex-maximal proper subgraphs of $C$ (which makes Property 3 of a DR-plan implicit.)
\end{definition}

\begin{definition}
    A DR-plan is \dfn{optimal} if it minimizes the maximum fan-in over all nodes in the forest. The maximum fan-in is called the \dfn{size} of the DR-plan.
\end{definition}

We denote these different kinds of DR-plans as $\drp{G}$, $\comdrp{G}$, and $\optdrp{G}$, respectively. Note that nodes will be referred to interchangeably as ``the node that represents or contains the (sub)graph $C$'' and as simply ``$C$''.

@@

See Figures \ref{fig:demo_graph}, \ref{fig:c2c3ofk33s}, \ref{fig:demo_graph:candrpseq}, \ref{fig:overconstrained}, and \ref{fig:bodypindrp} for examples of DR-plans and how their properties relate to each other.

>>>>

\ClearMyMinHeight
\SetMyMinHeight{.4}{../../img/svg/3xc2c3_new}
\SetMyMinHeight{.3}{../../img/svg/3xc2c3_new_comdrp}
\SetMyMinHeight{.3}{../../img/svg/3xc2c3_new_candrp}

\begin{figure*}\centering%

  \begin{subfigure}{0.4\linewidth}\centering
    \includegraphics[height=\myMinHeight]{../../img/svg/3xc2c3_new}
    \caption{}\label{fig:demo_graph:graph}
  \end{subfigure}%
  %
  \hfill
  \begin{subfigure}{0.3\linewidth}\centering
    \includegraphics[height=\myMinHeight]{../../img/svg/3xc2c3_new_comdrp}
    \caption{}\label{fig:demo_graph:comdrp}
  \end{subfigure}%
  %
  \hfill
  \begin{subfigure}{0.3\linewidth}\centering
    \includegraphics[height=\myMinHeight]{../../img/svg/3xc2c3_new_candrp}
    \caption{}\label{fig:demo_graph:candrp}
  \end{subfigure}%
  %
  % \begin{subfigure}[c]{0.3\linewidth}\centering
  %   \includegraphics[width=\linewidth]{../../img/svg/3xc2c3_new}
  %   \caption{}\label{fig:demo_graph:graph}
  % \end{subfigure}%
  % %
  % \hfill
  % \begin{subfigure}[t]{0.345\linewidth}\centering
  %   \includegraphics[width=\linewidth]{../../img/svg/3xc2c3_new_comdrp}
  %   \caption{}\label{fig:demo_graph:comdrp}
  % \end{subfigure}%
  % %
  % \hfill
  % \begin{subfigure}[t]{0.345\linewidth}\centering
  %   \includegraphics[width=\linewidth]{../../img/svg/3xc2c3_new_candrp}
  %   \caption{}\label{fig:demo_graph:candrp}
  % \end{subfigure}%
  %
  \caption{
  (\ref{fig:demo_graph:graph}) A graph, $G_{demo}$, used to illustrate concepts throughout this and the next section.
  %
  (\ref{fig:demo_graph:comdrp}) The complete DR-plan of $G_{demo}$.
  % i.e.\ $ComDRP(G_{demo})$.
  Dashed lines indicate that the children repeat the same pattern as the others shown on this level. The children of triangles (3 edges) are omitted.
  %
  (\ref{fig:demo_graph:candrp}) The canonical DR-plan of $G_{demo}$, which is optimal (see Section~\ref{sec:DRP}).
  % i.e.\ $OptDRP(G_{demo})$.
  The children of triangles are omitted.}
  \label{fig:demo_graph}
\end{figure*}%

@@

% \begin{definition}\label{def:drp}
%     The \dfn{decomposition-recombination \mbox{(DR-)} plan} \cite{hoffman2001decompositionI} of graph $G$, $\drp{G}$, is defined as a forest that has the following properties:
%     \begin{enumerate}
%         \item Each node represents/contains/is a rigid subgraph of $G$.
%         % \item For a node, $C$, that is  a non-trivial graph, its $N$
%         % children, $C_1, \ldots, C_N$, are rigid vertex-maximal proper
%         % subgraphs of $C$.
%         \item The children $C_1,\ldots,C_N$ of a node $C$ satisfy $\bigcup_{i=1}^N{C_i}=C$.
%         \item A leaf node is a single edge. A \dfn{trivial} graph is empty or a single vertex. Note that a trivial graph is not isostatic.
%         \item A root node is a vertex-maximal rigid subgraph of $G$.
%     \end{enumerate}
% %
%     % It can also be described recursively as: the root is $G$, its children are the trivial subgraphs and the DR-plans of its wellconstrained vertex-maximal proper subgraphs whose union is $G$ itself.
% %
%     A DR-plan is \dfn{complete} if it satisfies an additional property: for an internal node $C$, its children are all of the rigid vertex-maximal proper subgraphs of $C$. This makes Property 2 implicit.
%   %and in fact, $C$ contains all the edges in the union of its children as well.
%   We denote a complete DR-plan of $G$ as $\comdrp{G}$.

@@

\begin{definition}
[DR-plan]
\label{def:drp}
    A \dfn{decomposition-recombination \mbox{(DR-)} plan}~\cite{hoffman2001decompositionI} of graph $G$ is defined as a forest that has the following properties:
    \begin{enumerate}
        \item Each node represents a rigid subgraph of $G$.\footnote{Nodes will be referred to interchangeably as ``the node that represents or contains the (sub)graph $C$'' and as simply ``$C$''.}
        \item A root node is a vertex-maximal rigid subgraph of $G$.
        \item A node is the subgraph of $G$ induced by the union of its children.
        \item A leaf node is a single edge.
    \end{enumerate}
\end{definition}

Note that this definition permits the same rigid subgraph to appear in multiple nodes of the DR-plan. Not permitting such duplication would, in general, require the DR-plan to be defined as a directed acyclic graph instead of a forest.

\begin{definition}
[Complete DR-plan]
    A DR-plan is \dfn{complete} if it satisfies an additional property: for an internal node $C$, its children are all of the rigid vertex-maximal proper subgraphs of $C$ (which makes Property 3 of a DR-plan implicit).
\end{definition}

\begin{definition}
[Optimal DR-plan]
    A DR-plan is \dfn{optimal} if it minimizes the maximum fan-in over all nodes in the forest.
    % The maximum fan-in is called the \dfn{size} of the DR-plan.
\end{definition}

% We denote these different kinds of DR-plans as $\drp{G}$, $\comdrp{G}$, and $\optdrp{G}$, respectively.

@@

See Figures \ref{fig:demo_graph}, \ref{fig:c2c3ofk33s}, \ref{fig:demo_graph:candrpseq}, \todo{we lost this figure, replaced with \ref{fig:seqdrp_nonuniqueness}, should it be cited here now or should the other be added back in somewhere?} \ref{fig:overconstrained}, and \ref{fig:bodypindrp} for examples of DR-plans and how their properties relate to each other.
